WoS Crossref Journal Match

### 2019-10-11 analysis/wos_cr_match.Rmd
crossref journal and publisher name match

```{r}
#' search crossref
require(rcrossref)
jn_facets <- purrr::map(issns_list[66], .f = purrr::safely(function(x) {
  tt <- rcrossref::cr_works(
    filter = c(
      x,
      from_pub_date = "2014-01-01",
      until_pub_date = "2018-12-31",
      type = "journal-article"
    ),
    # being explicit about facets improves API performance!
    facet = "container-title:*,publisher-name:*",
    # less api traffic
    select = "DOI"
  )
  #' Parse the relevant information
  #' - `journal_title` - Crossref journal title (in case of journal name change, we use the most frequent name)
  #' - `publisher` - Crossref publisher (in case of publisher name change, we use the most frequent name)
  #'
  #' To Do: switch to current potential
  if (!is.null(tt)) {
    tibble::tibble(
      issn = list(x),
      journal_title = tt$facets$`container-title`$.id[1],
      publisher = tt$facets$publisher$.id[1]
    )
  } else {
    NULL
  }
}))
```

#' Dump:
jn_facets_df <- purrr::map_df(jn_facets, "result")
jsonlite::stream_out(jn_facets_df, file("../data/jn_facets_df.json"))

>>>>

```{r}
#' search crossref
require(rcrossref)
jn_facets <- plyr::llply(issns_list, purrr::safely(function(x) {
  tt <- rcrossref::cr_works(
    filter = c(
      x,
      from_pub_date = "2014-01-01",
      until_pub_date = "2018-12-31",
      type = "journal-article"
    ),
    # being explicit about facets improves API performance!
    facet = "container-title:*,publisher-name:*",
    # less api traffic
    select = "DOI"
  )
  #' Parse the relevant information
  #' - `journal_title` - Crossref journal title (in case of journal name change, we use the most frequent name)
  #' - `publisher` - Crossref publisher (in case of publisher name change, we use the most frequent name)
  #'
  #' To Do: switch to current potential
  if (!is.null(tt)) {
    tibble::tibble(
      issn = list(x),
      journal_title = tt$facets$`container-title`$.id[1],
      publisher = tt$facets$publisher$.id[1]
    )
  } else {
    NULL
  }
}), .progress = "text")
```

```{r}
#' Dump:
jn_facets_df <- purrr::map_df(jn_facets, "result")
cr_jn <- jn_facets_df %>% 
  unnest(issn)
readr::write_csv(cr_jn, "../data/cr_wos.csv")
```

#### ADD ISSN-L

```{r}
cr_journals <- readr::read_csv("../data/cr_wos.csv") %>%
  # merge springer nature brands
  mutate(publisher = ifelse(grepl("Springer", publisher, fixed = FALSE), "Springer Nature", publisher))
rp_country <- readr::read_csv("../data/rp_data_14_18.csv")
issn_l <- readr::read_tsv("../data/20190818.ISSN-to-ISSN-L.txt") %>%
  # manual fix Journal - American Water Works 
  add_row(ISSN = "2164-4535", `ISSN-L` = "0003-150X")
rp_df <- rp_country %>%
  left_join(issn_l, by = "ISSN") %>%
  left_join(cr_journals, by = c(ISSN = "issn")) %>%
  distinct()
```

#### Add OA info

```{r}
u <- "https://pub.uni-bielefeld.de/download/2934907/2934908/ISSN_Gold-OA_3.0.csv"
bie_oa <- readr::read_csv(u) %>%
  # remove missing entries with missing ISSN_L
  filter(!is.na(ISSN_L))
# add info to rp_df
rp_df_oa <- rp_df %>%
  mutate(oa_journal = `ISSN-L` %in% bie_oa$`ISSN_L`)
```
